Towards Contract Modules for the Tezos Blockchain

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex
Add files via upload

For the failure \lstinline/"to low"/, the analysis is very similar:
we need to know that there is no successful execution of
\lstinline/bid/ after an execution of \lstinline/close/. Moreover,
each invocation of \lstinline/bid/ raises the balance of the contract
monotonically. Thus, if the off-chain check
\lstinline/amount > balance/ fails, we can be sure that the contract
invocation will also fail; either because some closed the auction or
because the balance is at least as high as in the off-chain sample. 
\section{Related work}
\label{sec:related-work}
RPC APIs, often provided by current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper}, use loosely structured data, such as a JSON-based format, which is difficult for a programmatic program to handle. As a result, there is increasing work on providing better programmatic interfaces to the blockchains. Web3.js \cite{web3.js} provides an Ethereum JavaScript API and offers Java Script users a convenient interface to interact with the Etherum blockchain. Later, Web3.py \cite{web3.py}, derived from Web3.js, is developed to provide a Python library for interacting with Ethereum. Tezos prove a PRC API that utilizes JSON format for both input and output data, which is neither convenient nor programmatic.

Smart contract-based applications often require interaction between a smart contract on the blockchain and the outside world. However, smart contracts cannot connect to external sources on their own. This is where Oracles \cite{oracle-patterns,call-action-oracle,oracles-study} come into play. Oracles act as a bridge between smart contracts and external sources. Namely, they collect and verify external information and make it available to smart contracts on the blockchain. Oracles may need to observe the state of the chain to determine what information to send. Several research works have been conducted to provide oracle solutions for the Blockchain. Adler et al.\cite{blockchain-oracles} proposed a framework to provide developers with a guide for incorporating oracles into Blockchain-based applications. Practically, Ellis et al. \cite{chainlink-whitepaper} proposed the decentralized oracle network Chainlink to provide reliable, tamper-proof input for smart contracts on any blockchain. ChainLink securely provides data to APIs on behalf of a smart contract.

An oracle responds to an event by 
transmitting information to a smart contract through a smart contract invocation. In addition. the original smart contract must inherit an additional smart contract from Oracle in order to interact with external data sources. Deployment costs are increased when using Ethereum smart contracts with Oracle as the data carrier. To deal with this problem, the paper \cite{LIU2019590} proposes a low-cost data carrier architecture for a blockchain-enabled IoT environment.

>>>>

For the failure \lstinline/"to low"/, the analysis is very similar:
we need to know that there is no successful execution of
\lstinline/bid/ after an execution of \lstinline/close/. Moreover,
each invocation of \lstinline/bid/ raises the balance of the contract
monotonically. Thus, if the off-chain check
\lstinline/amount > balance/ fails, we can be sure that the contract
invocation will also fail; either because some closed the auction or
because the balance is at least as high as in the off-chain sample. 
\section{Related work}
\label{sec:related-work}
%RPC APIs, often provided by current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper}, use loosely structured data, such as a JSON-based format, which is difficult for a programmatic program to handle. As a result, there is increasing work on providing better programmatic interfaces to the blockchains. Web3.js \cite{web3.js} provides an Ethereum JavaScript API and offers Java Script users a convenient interface to interact with the Etherum blockchain. Later, Web3.py \cite{web3.py}, derived from Web3.js, is developed to provide a Python library for interacting with Ethereum. Tezos prove a PRC API that utilizes JSON format for both input and output data, which is neither convenient nor programmatic.

Smart contract-based applications often require interaction between a smart contract on the blockchain and the outside world. However, smart contracts cannot connect to external sources on their own. This is where oracles \cite{oracle-patterns,call-action-oracle} come into play. Oracles act as a bridge between smart contracts and external sources. Namely, they collect and verify external information and make it available to smart contracts on the blockchain. Several research works have been conducted to provide oracle solutions for the Blockchain. Adler et al.\cite{blockchain-oracles} proposed a framework to provide developers with a guide for incorporating oracles into blockchain-based applications. Oracles may need to observe the state of the chain to determine what information to send. In addition, oracles transmit data from external sources to the blockchain. Therefore, they would need to have a programmatic interface to interact with the blockchain. %Practically, Ellis et al. \cite{chainlink-whitepaper} proposed the decentralized oracle network Chainlink to provide reliable, tamper-proof input for smart contracts on any blockchain. ChainLink securely provides data to APIs on behalf of a smart contract.

%An oracle responds to an event by  transmitting information to a smart contract through a smart contract invocation. In addition. the original smart contract must inherit an additional smart contract from Oracle in order to interact with external data sources. Deployment costs are increased when using Ethereum smart contracts with Oracle as the data carrier. To deal with this problem, the paper \cite{LIU2019590} proposes a low-cost data carrier architecture for a blockchain-enabled IoT environment.

The basic idea of our advanced checking, namely precondition checking, is derived from the Java modeling language (JML)\cite{Leavens2006DesignBC, 101007}, in which the behavior of program components is described as an executable contract between Java program and its clients. This executable contract specifies preconditions that must be satisfied by clients and postconditions that are guaranteed by the program. A precondition supplied with a client call must be verified  before a function defined by the program is called, and the program guarantees that the postconditions are satisfied in return after the call. The original use of such preconditions and postconditions dades back to Hoare's paper on formal verification \cite{101145}. The executable contracts are written as program code in the programming language. In our approach, the safe contract module in the Ocaml language plays a role as an executable contract. Several applications are based on JML \cite{Tran2017, keY}. Ahrendt et al. \cite{keY} propose a framework called The KeY for deductive software verification.

Our contract module specifies preconditions and then off-chain checks whether a user call satisfies those preconditions. Symbolic execution plays an important role in the preconditions checking in our method. A smart contract is verified against its specification in the contract module by symbolic execution. In a paper on symbolic execution \cite{Hentschel}, Hentschel et al. proposed the symbolic execution debugger (SED) platform, which is based on the KeY framework. The platform SED has a static symbolic execution engine for sequential programs.
